The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-08-10 paper/paper.Rmd
Update references

```{r appendix2-plot, out.width="100%", fig.cap="Cross-validated RMSE estimates for 5 `comp_dist` competitive distances.", echo = FALSE}
mult_dist_comp %>%
  ggplot(aes(dist, rmse)) +
  geom_point() +
  xlab("Distance (m)") +
  ylab("RMSE (cm)")
```

@@

We observe in Figure \ref{fig:appendix2-code} that a cut-off distance of approximately 6m minimizes the cross-validation estimated RMSE.

>>>>

```{r appendix2-plot, out.width="100%", fig.cap="Cross-validated RMSE estimates for 5 competitive distances2.", echo = FALSE}
mult_dist_comp %>%
  ggplot(aes(dist, rmse)) +
  geom_point() +
  xlab("Distance (m)") +
  ylab("RMSE (cm)")
```

@@
